Compositional Certified Resource Bounds\ifshort{\vspace{-1.15cm}}{}

### 2014-11-12 paper/main.tex
add function specs paragraph

\jan{Here we have to say something about function specifications and
  function calls.}
\jan{Here we have to say something about function specifications and
  function calls.}
\jan{Here we have to say something about function specifications and
  function calls.}

>>>>

During the analysis, function specifications are quadruples
$(\Gamma_f, Q_f, \Gamma'_f, Q'_f)$ where $\Gamma_f, Q_f$ depend on
$\Vargs$, and $\Gamma'_f, Q'_f$ depend on $\Vret$.  These parameters
are instantiated by appropriate variables on call sites.  A distinctive
feature of our analysis is that it respects the function abstraction:
when deriving a function specification it generates a set of
constraints and the above quadruple; once done, the constraint
sets can readily be reused for every call site and the function need
not be analyzed multiple times.
